Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-08 shanghai.tex
I'm in the middle of the proposition on connected abelian algebraic groups.
Shown: all character sheaves on connected algebraic groups decend to
`bounded' character sheaves. Next I'll prove that all bounded character
sheaves are finite character sheaves on connected algebraic groups.

\section{Introduction}

@@

\section{The Picard group of character sheaves}\label{section:category}

%\input{category}
%\subsection*{Smooth commutative group schemes}

@@

%\subsection*{The category of character sheaves}

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
  sheaf on (the \'etale site of) $\bG$, locally constant of rank
  $1$ on connected components of $\bG$;

\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
  is an isomorphism of sheaves on $\bGxG$ such that

  \[
  \begin{tikzcd}[row sep=40]
  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
  \end{tikzcd}
  \]
  commutes, where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;

\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that

  \[
  \begin{tikzcd}
  \Frob_{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob_{\GxxG}^*\mu}
    && \Frob_{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob_{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
    && \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
    \bm^*\gcs{L} \arrow{rr}{\mu}
    && \LxL\\
  \end{tikzcd}
  \]
  commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such that
  \[
  \begin{tikzcd}[column sep=40]
  \Frob_G^* \gcs{L} \rar{\Frob_G^* \varphi} \arrow[swap]{d}{F} & \Frob_G^* \gcs{L'} \dar{F'}
  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
  \gcs{L} \rar{\varphi} & \gcs{L'}
  & {} & \LxL \rar{\tight{1}{\varphi\boxtimes \varphi}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
  \end{tikzcd}
  \]
  both commute.
\end{enumerate}

%\subsection*{The Picard group of character sheaves}

@@

%\subsection*{Trace of Frobenius}\label{sec:Frob}

@@

\begin{proposition}\label{prop:pullback}
  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
  $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
  \[
  \begin{tikzcd}[row sep=40]
   \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
  \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
  \end{tikzcd}
  \]
  is a commutative diagram of groups, where the lower homomorphism is
  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

@@

Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
If $(\cs{L}_0,\mu_0)$ is bounded character sheaf then $b_G^* \cs{L}_0$ comes equipped with an isomorphism $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^*\cs{L}_0$ which is compatible with $b_G^* \mu_0$, in the sense of Condition~\ref{CS.3}.
Thus, base change gives us a functor $b_G^* : \CS_f(G) \to \CS(G)$.
This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.

@@

\begin{proof}
 To prove the proposition we exhibit a fully faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
 %
 We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CS_0(G)$ 
 such that ${\bar L}(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
 Factoring along $C_1(G) \to \CS_0(G)$ will produce the full and faithful monoidal functor we seek.

@@

 Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
 it factors (uniquely!) through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
 to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
 Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full. 
 %
 Finally, we are ready to exhibit the full functor $L_G: \CS_b(G) \to \CS_0(G)$ promised above. 
 If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
 $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically.
 It follows immediately that 
  \[
  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS(G)
  \]
 is a fully faithfull monoidal functor, completing the proof.
\end{proof}

@@

\begin{proposition}\label{prop:connected-1}
  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then 
  the full subcategories $\CS_b(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
  appearing in Section~\ref{sec:bounded} are equivalences 
  and
  \[
  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
  \]
  is an isomorphism of groups.
\end{proposition}

\begin{proof}
 %Let $G$ be a geometrically connected algebraic group over $\Fq$.
  Observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
  sends character sheaves on $G$ to Weil local systems on
  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
  mean a Weil sheaf on $G$ which is a local system on $\bG$).
  While is it not true that all Weil local systems on $G$
  descend to local systems on $G$, we will see that those that appear in the image of the
  forgetful functor from character sheaves do. 
  Then we will see that these local systems further appear in the image of

  Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for
  $G$) and let $\bg$ be the geometric point on $G$ lying above
  $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). Since $G$ is
  geometrically connected, the geometric point $\bg$ determines
  an equivalence between the category of Weil local systems on $G$ and
  $\ell$-adic representations of $\W(G,\bg)$
  \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a
  character sheaf on $G$. Then the isomorphism class of the Weil local
  system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the
  Weil group $\W(G, \bg)$. The $\Fq$-rational point $g$ under
  the geometric point $\bg$ determines a splitting
  $\Weil{\Fq}\to \W(G,\bg)$ of the exact sequence
  \[
  \begin{tikzcd}
  1 \rar & \pi_1(\bG, \bg) \rar &  \W(G,\bg) \rar
  & \ar[swap,bend right, dotted]{l}{g} \Weil{\Fq} \rar & 1
  \end{tikzcd}
  \]
  In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character
  \[
  t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
  \]
  of the Weil group $\Weil{\Fq}$; the image of $\Frob$ under this
  character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.

  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EEx$
  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
  variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
  it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity,
  for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx$ is
  a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a
  finite subset of $\mu(\EE)$. Thus, $t_{(\gcs{L},F)}(g)$ extends to
  an $\ell$-adic character of $\Gal(\bFq/\Fq)$, which will be denoted
  by the same symbol.
  \[
  \begin{tikzcd}
  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \rar \dar & 1\\
  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1
  \end{tikzcd}
  \]

  We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EEx$
  to an $\ell$-adic character of $\pi_1(G,\bg)$ using the canonical topological group map
  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$, above. But $\bg$ also
  determines an equivalence between the category of $\ell$-adic
  representations of $\pi_1(G,\bg)$ and local systems on $G$. Let
  $\cs{L}_0$ be a local system on $G$ in the isomorphism class
  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
  Then $b^*\cs{L}_0 \iso \gcs{L}$, so $b^*$ is essentially surjective.

  We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence
  of rigid monoidal categories. It follows immediately that $b^*$
  determines an isomorphism
  \[
  b^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
  \]
  of the Picard groups determined by these rigid monoidal categories.
  \Clifton{\textdbend This last sentence glosses over some subtle points;
    I might need to address them in the `two perspectives' section.}

>>>>

\section*{Introduction}

@@

\section{The category of character sheaves}\label{section:category}

@@

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a rank-$1$ $\ell$-adic
  local system on (the \'etale site of) $\bG$;
\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
%
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
  \end{tikzcd}
  \]

%
\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
%
  \[
  \begin{tikzcd}[row sep=20]
  \Frob_{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob_{\GxxG}^*\mu}
    && \Frob_{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob_{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
    && \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
    \bm^*\gcs{L} \arrow{rr}{\mu}
    && \LxL\\
  \end{tikzcd}
  \]
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom_{\CS(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
  \[
  \begin{tikzcd}[column sep=40]
  \Frob_G^* \gcs{L} \rar{\Frob_G^* \varphi} \arrow[swap]{d}{F} & \Frob_G^* \gcs{L'} \dar{F'}
  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
  \gcs{L} \rar{\varphi} & \gcs{L'}
  & {} & \LxL \rar{\tight{1}{\varphi\boxtimes \varphi}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
  \end{tikzcd}
  \]
\end{enumerate}

\section{The Picard group of character sheaves}

@@

\section{Trace of Frobenius}\label{sec:Frob}

@@

\begin{proposition}\label{prop:pullback}
  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
  $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
  \[
  \begin{tikzcd}[row sep=30, column sep=30]
   \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
  \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
  \end{tikzcd}
  \]
  is a commutative diagram of groups, where the lower homomorphism is
  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

@@

Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
If $(\cs{L}_0,\mu_0)$ is bounded character sheaf then $b_G^* \cs{L}_0$ comes equipped with an isomorphism $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^*\cs{L}_0$ which is compatible with $b_G^* \mu_0$, in the sense of Condition~\ref{CS.3}.
Thus, base change gives us a functor $b_G^* : \CS_f(G) \to \CS(G)$.
This functor is full and faithful; see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}.

@@

\begin{proof}
 To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
 %
 We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CS_0(G)$ 
 such that ${\bar L}(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
 Factoring along $C_1(G) \to \CS_0(G)$ will produce the full and faithful monoidal functor we seek.

@@

 Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
 it factors (uniquely!) through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
 to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
 Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full. 
 %
 Finally, we are ready to exhibit the full functor $L_G: \CS_b(G) \to \CS_0(G)$ promised above. 
 If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
 $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically.
 It follows immediately that 
  \[
  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS_0(G)
  \]
 is a full and faithfull monoidal functor, completing the proof.
\end{proof}

@@

\begin{proposition}\label{prop:connected-1}
  If $G$ is a connected commutative algebraic group over $\Fq$ then 
  the full subcategories $\CS_f(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
  appearing in Section~\ref{sec:bounded} are equivalences 
  and
  \[
  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
  \]
  is an isomorphism of groups.
\end{proposition}

\begin{proof}
 %Let $G$ be a geometrically connected algebraic group over $\Fq$.
  Observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
  sends character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
  While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
  we will see that those that appear in the image of this forgetful functor from character sheaves do.

  Let $g$ be any $\Fq$-rational point on $G$ 
  and let $\bg$ be the geometric point on $G$ lying above $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). 
  Since $G$ is connected, the geometric point $\bg$ determines
  an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
  $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
  Now let $(\gcs{L},\mu,F)$ be a character sheaf on $G$ 
  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},F)$. 
  The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
  $\Weil{\Fq}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{\Fq}$. 
  In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
  %\[
  %\begin{tikzcd}
  %1 \rar & \pi_1(\bG, \bg) \rar &  \arrow{d}{\rho} \W(G,\bg) \rar
  %& \ar[swap,bend right, dotted]{l}{g} \arrow[dotted]{dl}{\rho_g} \Weil{\Fq} \rar & 1\\
  %&&\EEx&&
  %\end{tikzcd}
  %\]
  This character is given by the trace of Frobenius of $\cs{L}$ at $g$, as defined in Section~\ref{sec:Frob}:
  \[
  \rho_g(\Frob) =  t^\Frob_\cs{L}(g).
  \]

  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EEx$
  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
  variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
  it follows that $t^\Frob_\cs{L}(g) = \rho_g(\Frob)$ is a root of unity,
  for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
  $\Frob$ and $\rho_g : \Weil{\Fq} \to \EEx$ is
  a character, it follows that the image of $\rho_g$ is a finite group.
  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$, 
  denoted by the same symbol, below.
  \[
  \begin{tikzcd}
  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \arrow[bend left]{rr}{\rho_g} \rar \dar & 1 & \EEx\\
  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \arrow[dotted]{rru} \rar & 1 &
  \end{tikzcd}
  \]

  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
  to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$ determined by the structure map for $G$. But $\bg$ also
  determines an equivalence between the category of $\ell$-adic
  representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
  $\cs{L}_0$ be a local system on $G$ in the isomorphism class
  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
  Then $b_G^*\cs{L}_0 \iso \gcs{L}$.
  Since $b_G^*$ is full and faithful (again, see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}),
  $
  b_G^* : \Hom(m^*\cs{L}_0,\cs{L}_0\boxtimes\cs{L}_0) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
  $ 
  is a bijection. Let $\mu_0 : m^*\cs{L}_0 \to \cs{L}_0\boxtimes\cs{L}_0$ be the isomorphism matching 
  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$, from the definition of $\cs{L}$. 
  Then $(\cs{L}_0,\mu_0)$ is an object in $\CS_0(G)$ 
  and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_G^*\mu_0)$ in $\CS(G)$.
  Thus, $b_G^* : \CS_0(G) \to \CS(G)$ is essentially surjective.

  \todo{Clifton is here. I will use \cite{Kamgarpour} to finish the proof.}

  We have now shown that $b_G^* : \CS_0(G) \to \CS(G)$ is an equivalence
  of rigid monoidal categories. It follows immediately that $b_G^*$
  determines an isomorphism
  \[
  b_G^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
  \]
  of the Picard groups determined by these rigid monoidal categories.
  \Clifton{\textdbend This last sentence glosses over some subtle points;
    I might need to address them in the `two perspectives' section.}
